---
title: "SQL"
output: html_document
---

## Filtering columns and rows

With SQL, you can filter columns and rows by using Select and where. Let's look at an example using Lahman database.

```{r,message=FALSE,warning=FALSE}
library(Lahman)

library(sqldf)
```


Supose now  I would like to see the homerun totals for the 1927 Yankees. I could write the following query:

```{r}
query <-"select playerID,yearID,teamID,hr from Batting
WHERE teamID='NYA' and yearID=1927"
sqldf(query)
```
##Phillies batting from 1770

```{r}
query <-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='PHI' and HR>30 and yearID<=1979 and yearID>=1970"

sqldf(query)
```


## Order By

with SQL, you can order the rows of your output. For instance,suppose you want to see every instance of a player hitting more than 50 homeruns. But you would like players with the most homeruns to be at the top. We could do the following:
```{r}
query <-"SELECT playerID,yearID,teamID,Hr FROM Batting
WHERE HR>50
ORDER BY HR DESC"
sqldf(query)
```





